Summary

### 2015-10-14 inst/examples/Vaasa.Rmd
more refactoring

```{r, echo=FALSE, message=FALSE}
# data ei välttämättä lopullinen
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(published_in))
vaasa1 <- df %>% filter(city == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
vaasa1$decade <- as.numeric(paste0(substr(vaasa1$published_in,1,3),"0"))
vaasa2 <- vaasa1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
vaasa <- inner_join(vaasa1,vaasa2)
```

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1800,1840,1880,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```

>>>>

```{r, echo=FALSE, message=FALSE}
# data ei välttämättä lopullinen
df <- readRDS("df.Rds")
df <- df %>% filter(!is.na(published_in))
tmp1 <- df %>% filter(publication_place == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
tmp1$decade <- as.numeric(paste0(substr(tmp1$published_in,1,3),"0"))
tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
final <- inner_join(tmp1,tmp2)
```

```{r Vaasa, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(final$published_in,final$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(final$published_in,final$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```

```{r, echo=FALSE}
remove(tmp1,tmp2,final)
```

### 2015-10-14 inst/examples/summary.Rmd
more refactoring

df <- readRDS("df.RData")

@@

# List all topics
spl <- strsplit(na.omit(as.character(df$term_topic)), ";")

@@

```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geography), ";")))))
```

Top-`r ntop` geographical places are shown together with the number of documents assigned to that region. Geography information is available for `r sum(!is.na(df$term_geography))` documents (`r round(100*mean(!is.na(df$term_geography)))`%). There are `r length(tab)` unique geographical places.

@@

Top-`r ntop` publication places are shown together with the number of documents. This info is available for `r sum(!is.na(df$city))` documents (`r round(100*mean(!is.na(df$city)))`%). There are `r length(unique(str_trim(unlist(strsplit(as.character(df$city), ";")))))` unique publication places.

```{r city, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$city), ";"))))))
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
```

```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publicationplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

>>>>

df <- readRDS("df.Rds")

@@

# List all topics
spl <- strsplit(na.omit(as.character(df$subject_topic)), ";")

@@

```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$subject_geography), ";")))))
```

Top-`r ntop` geographical places are shown together with the number of documents assigned to that region. Geography information is available for `r sum(!is.na(df$subject_geography))` documents (`r round(100*mean(!is.na(df$subject_geography)))`%). There are `r length(tab)` unique geographical places.

@@

Top-`r ntop` publication places are shown together with the number of documents. This info is available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%). There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` unique publication places.

```{r publication_place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_place), ";"))))))
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
```

```{r publication_place2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publicationplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```
